%====================
% UCL Robotics Intern
%====================
\subsection*{{
    UCL Computer Science Robotics Internship
    \hfill 06/2022 - 09/2022
}}
\subtext{
    Supervised by Prof. Simon Julier, Prof. Dimitrios Kanoulas, Prof. Francisco Porto Guerra E Vasconcelos and \newline Prof. Eddie Edwards
}
\begin{zitemize}
    \item   Conducted a series of experiments on mycobot robot developed by ElephantRobotics 
            to prepare for new modules (COMP0128, COMP0129, and COMP0130) at UCL Computer Science. 
            Tested the installation and usage of ROS Noetic at different operating systems and architectures to provide a comprehensive installation guidance and 
            created simulated environment in Gazebo. 
            Also implemented ros packages to (1) calibrate its joint position
            (2)communicate with the mycobot robot to read its status and send instructions
            (3)read and visualize sensor data (camera, lidar, …),
            (4)move the arm to specific locations in robot coordinates
            (5)follow the visual tracking markers (aruco)
    \item   Available on Github repository 
            \url{https://github.com/t1mkhuan9/mycobot_ros}
\end{zitemize}


%====================
% System Engineering 
%====================
\subsection{{
    Recyclone Mobile App Team Leader
    \hfill 10/2020 --- 05/2021
}}
\subtext{
    Supervised by Mr. Hardwick James at University College London and Mr. Fergus Kidd at Avanade 
}
\begin{zitemize}
    \item   As a team of 3, created an app to encourage people recycle unused materials by showing
            the drop-off position of the identified item and giving 'points' to them
            once they have completed one recycle. 
    \item   Developed and Deployed a SpringBoot backend providing RESTful APIs.
            Used Azure Computer Vision API to accomplish item identifying tasks.
            Used MySQL Server to store account details. 
    \item   Created the item identifying page and the scoreboard page in the Flutter app and connected it
            to the backend. Helped teammates with other pages when necessary. 
    \item   Organize team's weekly tasks and prepare a weekly report to clients. 
    \item   Video Introduction can be found on \href{https://www.youtube.com/watch?v=gh0Uv4mf7cA&t=3s&ab_channel=timkhuang}{youtube}.
    \item   Received 1st Class Distinction result
\end{zitemize}


%====================
% Citrix
%====================
\subsection{{
    Citrix Summer Intern
    \hfill 07/2020 --- 08/2020
}}
\subtext{
    Supervised by Senior Software Engineer Mr. Dan Hu
}
\begin{zitemize}
    \item   Created a chrome extension with JavaScript to capture unsafe events
            happened in the Citrix Workspace, such as pop-up windows. 
            Stored the data in a sqlite database and provided a comprehensive
            analysis website.
    \item   Received the Silver Award for the project and the Campus Star Award for myself.
\end{zitemize}


%====================
% China Mobile
%====================
\subsection{{
    China Mobile AI Department Intern
    \hfill 04/2020 --- 06/2020
}}
\subtext{
    Supervised by Senior Reseacher Mr. Xiaoming Ma and Mr. Qiang Gu
}
\begin{zitemize}
    \item   Conducted researches on company seals recognition and classification.
            Provided weekly research report.
            Implemented ELSDc algorithm along with OpenCv library. 
            Collected company seals images and succeeded to train a neural network with assistance from supervisors.
\end{zitemize}


%====================
% UCollege X 
%====================
\subsection{{
    UCollege X Mobile App
    \hfill 01/2020 --- 05/2020
}}
\subtext{
    Self-motivated Development Project
}
\begin{zitemize}
    \item   Scraped university ranking data with python and selenium from QS ranking,
            Times Raking and US News Ranking.
            Written Flutter App to visualize data stored in the sqlite database.
            Plotted graphs for each universities ranking details (1) at each year
            (2) at different ranking websites, (3) of different majors.
    \item   Published on Apple App store and Google Play store until developer account expired.
\end{zitemize}
